\speculake: Hiding Malware in Speculative Execution

### 2018-05-07 paper/figures.tex
update captions
VM implementation updates

\newcommand{\FigSpecMeasure}{
\begin{figure*}[t]
    \centering
        \includegraphics[width=0.9\textwidth]{figures/Speculative_measurements.png}
    \caption{The speculative primitive allows for a limited number of instructions
        to be completed speculatively, dependent on multiple factors. Trigger and 
        payload processes must share cpu resources as they must be performed on 
        the same hyperthread or associated parity hyperthreads. Processes on
        the parity hyperthreads (warm colors) denoted by (P) accomplish a 
        significantly lower number of instructions as compared with processes 
        on the same hyperthread (cool colors).}
    \label{fig:spec-capacity}
\end{figure*}
}

\newcommand{\FigCacheMiss}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/cache_miss_dist}
    \caption{Cache Hit/Miss Latency Distribution}
    \label{fig:cache-miss}
\end{figure}
}

>>>>

\newcommand{\FigSpecMeasure}{
\begin{figure*}[t]
    \centering
        \includegraphics[width=0.9\textwidth]{figures/Speculative_measurements.png}
    \caption{The speculative primitive allows for a limited number of instructions
        to be completed speculatively, dependent on multiple factors. Trigger and 
        payload processes must share CPU resources as they must be performed on 
        the same hyperthread or associated parity hyperthreads. Processes on
        the parity hyperthreads (warm colors) denoted by (P) accomplish a 
        significantly lower number of instructions as compared with processes 
        on the same hyperthread (cool colors).}
    \label{fig:spec-capacity}
\end{figure*}
}

\newcommand{\FigCacheMiss}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/cache_miss_dist}
    \caption{The Cache Hit/Miss Latency Distribution of an Intel
        Xeon-1270. Measured by timing accesses to cached/uncached memory. 
        Typical cache miss resolution takes 6x longer than a cache hit.}
    \label{fig:cache-miss}
\end{figure}
}
